An Empirical Analysis of the Role of Energy in Economic Growth

### 2014-12-24 Articles/Article_EnerEcon_2014/EconGrowth3.Rnw
US Elasticities of substitution table complete.

\begin{table} \caption{Example economies and years of evaluation.} \label{tab:Economy_Examples} 
  \begin{center}
    \begin{tabular}{r c c l l} 
      \multirow{3}{*}{Developed} & \includegraphics[height=0.11in]{flag/flag_US.png} & US & USA & \multirow{3}{*}{1980--2011}\\
                                 & \includegraphics[height=0.11in]{flag/flag_UK.png} & UK & United Kingdom & \\
                                 & \includegraphics[height=0.11in]{flag/flag_JP.png} & JP & Japan          & \\
      \hline
      \multirow{2}{*}{NICs}      & \includegraphics[height=0.11in]{flag/flag_CN.png} & CN & China & \multirow{2}{*}{1991--2011}        \\
                                 & \includegraphics[height=0.11in]{flag/flag_ZA.png} & ZA & South Africa & \\
      \hline
      \multirow{2}{*}{OPEC}      & \includegraphics[height=0.11in]{flag/flag_SA.png} & SA & Saudi Arabia & \multirow{2}{*}{1991--2011} \\
                                 & \includegraphics[height=0.11in]{flag/flag_IR.png} & IR & Iran         &  \\
      \hline
      \multirow{2}{*}{LDCs}      & \includegraphics[height=0.11in]{flag/flag_TZ.png} & TZ & Tanzania & \multirow{2}{*}{1991--2011}     \\
                                 & \includegraphics[height=0.11in]{flag/flag_ZM.png} & ZM & Zambia      & \\
    \end{tabular}
  \end{center}
\end{table}

@@

\begin{table} \caption{Equations for $\alpha$, $\beta$, and $\gamma$ for the various CES nestings.} 
\label{tab:CES_abg_equations} 
  \begin{center}
    \begin{tabular}{c c c c c} 
      Nesting    & Equation        & $\alpha$                & $\beta$                 & $\gamma$                     \\
      \hline
      ($kl$) + ()     & \ref{eq:CES}    & $\delta_1$              & $1 - \delta_1$          & 0                       \\
      ($kl$) + ($e$)  & \ref{eq:CESkle} & $\delta \delta_1$       & $\delta (1 - \delta_1)$ & $1 - \delta$            \\   
      ($le$) + ($k$)  & \ref{eq:CESlek} & $1 - \delta$            & $\delta \delta_1$       & $\delta (1 - \delta_1)$ \\
      ($ek$) + ($l$)  & \ref{eq:CESekl} & $\delta (1 - \delta_1)$ & $1 - \delta$            & $\delta \delta_1$       \\
    \end{tabular}
  \end{center}
\end{table}

@@

\begin{table} \caption{Elasticities of substitution (US).} \label{tab:sigma_US} 
  \begin{center}
    \begin{tabular}{r l l l} 
      \toprule
      & $k$ \& $l$ & $k$ \& $e$ & $l$ \& $e$ \\
      \midrule
      \multirow{2}{*}{$\sigma_1$} & ($\underline{kl}$): C 
                                        & 
                                              &  \\
                                  & ($\underline{kl}$)$e$: C 
                                        & ($\underline{ek}$)$l$: $\sim\sim\sim$ 
                                              & ($\underline{le}$)$k$: $\sim\sim\sim$ \\
      \midrule
      \multirow{3}{*}{$\sigma$} & 
                                      & ($\underline{k}l$)$\underline{e}$: $\sim\sim\sim$
                                            & ($k\underline{l}$)$\underline{e}$: $\sim\sim\sim$ \\
                                & ($\underline{l}e$)$\underline{k}$: C
                                      & ($l\underline{e}$)$\underline{k}$: C
                                            &  \\
                                & ($e\underline{k}$)$\underline{l}$: C
                                      & 
                                            & ($\underline{e}k$)$\underline{l}$: C \\
      \bottomrule
%       \multirow{2}{*}{$sigma_1$}  & ($kl$): C        &                           &                           \\
%                                   & ($kl$)$e$: C     & ($ek$)$l$: $\var\var\var$ & ($le$)$k$: $\var\var\var$ \\
% 
% 
%       \multirow{3}{*}{Developed} & \includegraphics[height=0.11in]{flag/flag_US.png} & US & USA & \multirow{3}{*}{1980--2011}\\
%                                  & \includegraphics[height=0.11in]{flag/flag_UK.png} & UK & United Kingdom & \\
%                                  & \includegraphics[height=0.11in]{flag/flag_JP.png} & JP & Japan          & \\
%       \hline
%       \multirow{2}{*}{NICs}      & \includegraphics[height=0.11in]{flag/flag_CN.png} & CN & China & \multirow{2}{*}{1991--2011}        \\
%                                  & \includegraphics[height=0.11in]{flag/flag_ZA.png} & ZA & South Africa & \\
%       \hline
%       \multirow{2}{*}{OPEC}      & \includegraphics[height=0.11in]{flag/flag_SA.png} & SA & Saudi Arabia & \multirow{2}{*}{1991--2011} \\
%                                  & \includegraphics[height=0.11in]{flag/flag_IR.png} & IR & Iran         &  \\
%       \hline
%       \multirow{2}{*}{LDCs}      & \includegraphics[height=0.11in]{flag/flag_TZ.png} & TZ & Tanzania & \multirow{2}{*}{1991--2011}     \\
%                                  & \includegraphics[height=0.11in]{flag/flag_ZM.png} & ZM & Zambia      & \\
    \end{tabular}
  \end{center}
\end{table}

>>>>

\begin{table} \caption{Example economies and years of evaluation.} \label{tab:Economy_Examples} 
  \begin{center}
    \begin{tabular}{r c c l l} 
      \toprule
      \multirow{3}{*}{Developed} & \includegraphics[height=0.11in]{flag/flag_US.png} & US & USA & \multirow{3}{*}{1980--2011}\\
                                 & \includegraphics[height=0.11in]{flag/flag_UK.png} & UK & United Kingdom & \\
                                 & \includegraphics[height=0.11in]{flag/flag_JP.png} & JP & Japan          & \\
      \midrule
      \multirow{2}{*}{NICs}      & \includegraphics[height=0.11in]{flag/flag_CN.png} & CN & China & \multirow{2}{*}{1991--2011}        \\
                                 & \includegraphics[height=0.11in]{flag/flag_ZA.png} & ZA & South Africa & \\
      \midrule
      \multirow{2}{*}{OPEC}      & \includegraphics[height=0.11in]{flag/flag_SA.png} & SA & Saudi Arabia & \multirow{2}{*}{1991--2011} \\
                                 & \includegraphics[height=0.11in]{flag/flag_IR.png} & IR & Iran         &  \\
      \midrule
      \multirow{2}{*}{LDCs}      & \includegraphics[height=0.11in]{flag/flag_TZ.png} & TZ & Tanzania & \multirow{2}{*}{1991--2011}     \\
                                 & \includegraphics[height=0.11in]{flag/flag_ZM.png} & ZM & Zambia      & \\
      \bottomrule
    \end{tabular}
  \end{center}
\end{table}

@@

\begin{table} \caption{Equations for $\alpha$, $\beta$, and $\gamma$ for the various CES nestings.} 
\label{tab:CES_abg_equations} 
  \begin{center}
    \begin{tabular}{c c c c c} 
      \toprule
      Nesting    & Equation        & $\alpha$                & $\beta$                 & $\gamma$       \\
      \midrule
      ($kl$) + ()     & \ref{eq:CES}    & $\delta_1$              & $1 - \delta_1$          & 0          \\
      ($kl$) + ($e$)  & \ref{eq:CESkle} & $\delta \delta_1$       & $\delta (1 - \delta_1)$ & $1 - \delta$ \\   
      ($le$) + ($k$)  & \ref{eq:CESlek} & $1 - \delta$            & $\delta \delta_1$       & $\delta (1 - \delta_1)$ \\
      ($ek$) + ($l$)  & \ref{eq:CESekl} & $\delta (1 - \delta_1)$ & $1 - \delta$            & $\delta \delta_1$ \\
      \bottomrule
    \end{tabular}
  \end{center}
\end{table}

@@

\begin{table} \caption{Elasticities of substitution (US).} \label{tab:sigma_US} 
  \begin{center}
    \begin{tabular}{r l c l c l c} 
      \toprule
         & \multicolumn{2}{c}{$k$ \& $l$} & \multicolumn{2}{c}{$k$ \& $e$} & \multicolumn{2}{c}{$l$ \& $e$} \\
      \midrule
      \multirow{2}{*}{$\sigma_1$} & ($\underline{kl}$) & C 
                                        &  & 
                                              & &  \\
                                  & ($\underline{kl}$)$e$ & C 
                                        & ($\underline{ek}$)$l$ & $\sim\sim\sim$ 
                                              & ($\underline{le}$)$k$ & $\sim\sim\sim$ \\
      \midrule
      \multirow{3}{*}{$\sigma$} & &
                                      & ($\underline{k}l$)$\underline{e}$ & $\sim\sim\sim$
                                            & ($k\underline{l}$)$\underline{e}$ & $\sim\sim\sim$ \\
                                & ($\underline{l}e$)$\underline{k}$ & C
                                      & ($l\underline{e}$)$\underline{k}$ & C
                                            &  & \\
                                & ($e\underline{k}$)$\underline{l}$ & C
                                      & &
                                            & ($\underline{e}k$)$\underline{l}$ & C \\
      \midrule
                                & \multicolumn{2}{c}{C} & \multicolumn{2}{c}{C} & \multicolumn{2}{c}{C} \\
      \bottomrule
    \end{tabular}
  \end{center}
\end{table}
